Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-31 W13report.tex
Minor word change

We
investigated the complexity of the basis functions used to model
the PSF--matching kernel, and the degree to which this kernel varies
across the images.  We generated several goodness of fit statistics
for a control sample of sources that were {\it not} used in the kernel
fit, in order to assess the interpolation ability of the matching
kernel.  These metrics are shown to correlate with the numbers of false positives.  
We calculate a mean squared error metric that shows a minimum close to the configurations
that yielded the lowest number of false positives, and shows promise as a means
to algorithmically choose the optimal pipeline configuration.

>>>>

We
investigated the complexity of the basis functions used to model
the PSF--matching kernel, and the degree to which this kernel varies
across the images.  We generated several goodness of fit statistics
for a control sample of sources that were {\it not} used in the kernel
fit, in order to assess the interpolation ability of the matching
kernel.  These metrics are shown to correlate with the numbers of false positives.  
We calculate a mean squared error metric that shows a minimum value close to the configurations
that yielded the lowest number of false positives, and shows promise as a means
to algorithmically choose the optimal pipeline configuration.
